---
title: "Audit everything"
subtitle: "Registry-wide replication health check"
author: "replicate-anything/registry"
embed-resources: true
date: last-modified
params:
  patience: 60
  install_deps: false
  dois: !expr NULL
  collections: !expr NULL
  refresh: true
execute:
  echo: false
  warning: false
  message: false
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    theme: flatly
---

```{r setup}
#| include: false
knitr::opts_chunk$set(comment = NA)

registry_root <- normalizePath(getwd(), winslash = "/", mustWork = FALSE)
if (!file.exists(file.path(registry_root, "index.csv"))) {
  stop(
    "Render from the registry repository root (expected index.csv in working directory).",
    call. = FALSE
  )
}

if (!requireNamespace("replicateEverything", quietly = TRUE)) {
  monorepo <- Sys.getenv("REPLICATE_MONOREPO", unset = "")
  if (!nzchar(monorepo)) {
    parent <- normalizePath(file.path(registry_root, ".."), winslash = "/", mustWork = FALSE)
    if (file.exists(file.path(parent, "replicateEverything", "DESCRIPTION"))) {
      monorepo <- parent
    }
  }
  pkg_path <- if (nzchar(monorepo)) file.path(monorepo, "replicateEverything") else ""
  if (nzchar(pkg_path) && file.exists(file.path(pkg_path, "DESCRIPTION")) &&
      requireNamespace("devtools", quietly = TRUE)) {
    devtools::load_all(pkg_path, quiet = TRUE)
  }
}
if (!requireNamespace("replicateEverything", quietly = TRUE)) {
  stop(
    "Install replicateEverything before rendering this report, e.g.\n",
    "  remotes::install_github('replicate-anything/replicateEverything')\n",
    "Or set REPLICATE_MONOREPO to a checkout that contains replicateEverything/.",
    call. = FALSE
  )
}

library(replicateEverything)
options(replicateEverything.registry_root = registry_root)

patience <- if (is.null(params$patience)) 20 else params$patience
install_deps <- isTRUE(params$install_deps)
dois <- params$dois
collections <- params$collections
refresh <- if (is.null(params$refresh)) TRUE else isTRUE(params$refresh)
audit_rds <- file.path(registry_root, "audit_latest.rds")

if (!refresh && file.exists(audit_rds)) {
  audit <- readRDS(audit_rds)
  message("Loaded audit from ", audit_rds)
} else {
  audit <- audit_everything(
    patience = patience,
    dois = dois,
    collections = collections,
    install_deps = install_deps,
    verbose = TRUE,
    registry_root = registry_root
  )
}

results <- audit$results
summary <- audit$summary
```

This report uses [`audit_everything()`](https://github.com/replicate-anything/replicateEverything) from the **replicateEverything** package. It walks this registry and attempts every table and figure in each listed engine (R and Stata where both exist). Incomplete / blocked steps (`incomplete: true`, missing `requires_engine:`, or `data_unavailable:`) are recorded as **Skipped** and are not executed. A runnable job is halted after **`r patience`** seconds (the audit cap); timeout rows say so explicitly (`timeout_seconds` in the results). Failures are recorded and the audit continues.

```{r collections-note}
#| echo: false
#| results: asis
if (!is.null(collections) && length(collections) > 0L) {
  cat(sprintf(
    "\n\n**Collections filter:** %s\n\n",
    paste(collections, collapse = ", ")
  ))
}
```

**Started:** `r format(audit$started_at, "%Y-%m-%d %H:%M:%S %Z")`  
**Finished:** `r format(audit$finished_at, "%Y-%m-%d %H:%M:%S %Z")`

## Summary

| Metric | Count |
|:--|--:|
| Studies audited | `r summary$studies` |
| Replication runs | `r summary$runs` |
| Successful | `r summary$success` |
| Failed | `r summary$failed` |
| Timed out | `r summary$timed_out` |
| Skipped | `r summary$skipped %||% 0L` |
| Substantive failed | `r summary$substantive_failed %||% 0L` |

When a study defines `tests/substantive/<step_id>.R`, the audit compares replicated estimates to published benchmarks (Fearon & Laitin `tab_1` is the reference). Failures are counted separately and marked `[substantive]` in the console summary.

```{r summary-bar}
#| echo: false
attempted <- summary$runs - (summary$skipped %||% 0L)
if (attempted > 0) {
  pct <- round(100 * summary$success / attempted, 1)
  cat(sprintf("**Pass rate (excluding skipped):** %s%%\n\n", pct))
}
```

## Results by study

```{r by-study}
#| results: asis
if (nrow(results) == 0) {
  cat("_No replication runs were recorded._\n")
} else {
  if (!"skipped" %in% names(results)) {
    results$skipped <- FALSE
  }
  studies <- unique(results$title)
  for (study in studies) {
    cat("\n\n### ", study, "\n\n", sep = "")
    sub <- results[results$title == study, , drop = FALSE]
    sub$status <- audit_result_status(sub$success, sub$timed_out, sub$skipped)
    sub$seconds <- ifelse(is.na(sub$seconds), NA, round(sub$seconds, 2))
    cols <- c(
      "object_label", "object", "type", "engine",
      "status", "seconds", "error_snippet"
    )
    if ("timeout_seconds" %in% names(sub)) {
      cols <- c(
        "object_label", "object", "type", "engine",
        "status", "seconds", "timeout_seconds", "error_snippet"
      )
    }
    show <- sub[, cols, drop = FALSE]
    names(show) <- if ("timeout_seconds" %in% cols) {
      c(
        "Object", "ID", "Type", "Engine",
        "Status", "Seconds", "Cap (s)", "Error"
      )
    } else {
      c(
        "Object", "ID", "Type", "Engine",
        "Status", "Seconds", "Error"
      )
    }
    print(knitr::kable(show, format = "html", na = ""))
  }
}
```

## Failed runs (concise)

```{r failures}
#| echo: false
if (!"skipped" %in% names(results)) {
  results$skipped <- FALSE
}
fails <- results[results$success %in% FALSE & !results$skipped %in% TRUE, , drop = FALSE]
if (nrow(fails) == 0) {
  cat("_All recorded runnable jobs succeeded (or were skipped)._\n")
} else {
  fails$seconds <- ifelse(is.na(fails$seconds), NA, round(fails$seconds, 2))
  fails$status <- audit_result_status(fails$success, fails$timed_out, fails$skipped)
  fail_cols <- c(
    "title", "object_label", "object", "engine",
    "status", "seconds", "error_snippet"
  )
  fail_names <- c(
    "Study", "Object", "ID", "Engine",
    "Status", "Seconds", "Error"
  )
  if ("timeout_seconds" %in% names(fails)) {
    fail_cols <- c(
      "title", "object_label", "object", "engine",
      "status", "seconds", "timeout_seconds", "error_snippet"
    )
    fail_names <- c(
      "Study", "Object", "ID", "Engine",
      "Status", "Seconds", "Cap (s)", "Error"
    )
  }
  show <- fails[, fail_cols, drop = FALSE]
  names(show) <- fail_names
  knitr::kable(show, format = "html", na = "")
}
```

## Skipped runs (incomplete / unavailable)

```{r skips}
#| echo: false
if (!"skipped" %in% names(results)) {
  results$skipped <- FALSE
}
skips <- results[results$skipped %in% TRUE, , drop = FALSE]
if (nrow(skips) == 0) {
  cat("_No steps were skipped as incomplete / unavailable._\n")
} else {
  skips$status <- "Skipped"
  show <- skips[, c(
    "title", "object_label", "object", "engine",
    "status", "error_snippet"
  )]
  names(show) <- c(
    "Study", "Object", "ID", "Engine",
    "Status", "Reason"
  )
  knitr::kable(show, format = "html", na = "")
}
```

## Re-run

From this registry checkout:

```bash
quarto render audit_everything.qmd -P patience:30
```

Re-render HTML from saved results (no live re-run):

```bash
Rscript scripts/run_audit.R
quarto render audit_everything.qmd -P refresh:false
```

```{r, eval = FALSE}
library(replicateEverything)
options(replicateEverything.registry_root = normalizePath(getwd()))
audit <- audit_everything(patience = 20)
print(audit)
```

Subset of studies:

```r
quarto::quarto_render(
  replicateEverything::audit_everything_qmd(),
  execute_params = list(
    patience = 20,
    dois = c("10.1177/00491241211036161")
  )
)

# One collection (e.g. APSR studies only)
quarto::quarto_render(
  replicateEverything::audit_everything_qmd(),
  execute_params = list(patience = 20, collections = "APSR")
)
```

Update the package vignette snapshot after a full audit:

```r
saveRDS(audit, "<path-to-replicateEverything>/inst/vignette-data/audit_latest.rds")
```

The audit also writes `audit_summary.json` and `audit_latest.rds` in this registry repo (used by the Shiny health bar).
